# Question 3


```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
source('r/pre-processing.r')

j1  <- f1[edgrp == '4']

``` 


#### q3.a


I find it to be a relevant critique, since the error term might be correlated to the explanatory variable of PC use - Since the wage gap happening as a process *leading up to* the year 2000*, there is good reason to suspect that the PC has a systematic relation to the error term. 




#### q3.b

The cofficent for this approach is ~ -.5, and it it is signifant at the 5 % level.



``` {r,  echo=FALSE, message=FALSE, warning=FALSE}

q3b <- feols(dmfwg28 ~ durmf1980 + nondmf1980 | pcemp_m_c2000 ~ lncs1980 , data = j1, vcov='hetero')
q3b  %>% etable()
```


#### q3.c 

the relevance is evaluated by calculating the correlation between the instrument and the possible endogeneous variable  and testing for significance. There is a highly signicant result between them. However, somewhat puzzling, there is not between pc use and the wage gap in this educational group, which I included as a check. 

there is however also a signicant but somewhat smaller correlation between the instrument and the wage gap, which is not a good sign. 


regressing the instrument and the controls on the pc use variable, we get a signicant result, meaning that the instrument does predict pc use. 

``` {r,  echo=FALSE, message=FALSE, warning=FALSE}




j1[, .(pcemp_m_c2000, lncs1980, dmfwg28)] %>% dtcor() 
feols(pcemp_m_c2000 ~ lncs1980 + durmf1980 + nondmf1980, data = j1, vcov='hetero') %>% etable()


```

The hauseman test, showing the validity of the IV approach, is also signicant (it's prinited at the end of the output.)




``` {r,  echo=FALSE, message=FALSE, warning=FALSE}
q3b  
```

All in all, I conclude that the IV approach seems to be valid, but the correlation between the instrument and the wage gap in the primary model is concerning.

#### q3.d


first the IV model, next to the naive ols model and the previous IV model with only one instrument. We see that the parameter of interest looses power, going from -.5 to -.29, and is no longer significant.

``` {r,  echo=FALSE, message=FALSE, warning=FALSE}


q3b_naive <- feols(dmfwg28 ~ durmf1980 + nondmf1980 + pcemp_m_c2000,  data = j1, vcov='hetero')
q3e <- feols(dmfwg28 ~ durmf1980 + nondmf1980 | pcemp_m_c2000 ~ lncs1980 +  lnlf1980 + mexish1980 , data = j1, vcov='hetero')
etable(q3b_naive, q3b, q3e)


```

next an overidentification test, which is not significant, meaning the instruments are not valid. 

``` {r,  echo=FALSE, message=FALSE, warning=FALSE}

# overidentification test (can only be done with >= 2 instruments)
j1[, iv_res := resid(q3e)]

mod_overid  <- feols(iv_res ~  lncs1980 +  lnlf1980 + mexish1980 + durmf1980 + nondmf1980   , j1 )

oid <- r2(mod_overid)[['r2']] * nrow(j1) 

# not getting the right chisq value, not sure why 
pchisq(oid, df= 1)


```

#### q3.e




